Proposed Solution

### 2017-04-18 OOPSLA17/secs/intro.tex
ruzica part 1

Our main task was to first derive a specification for configuration 
files. We first process a \ruzica{mention the size, size does matter :)}training set of configuration files. Those files are benchmarks 
available on-line~\ruzica{put a citation here}. They are mostly correct
but they also may contain some errors.

In order to learn a specification from this large set of configuration
files,
the first step is to 
translate the training set into a more structured typed representation.
We then apply the learning process and we learn an abundant set of rules 
specifying various properties that hold on the given training set. 
\ruzica{say here 2 sentences about the learning process }

>>>>

Our main task was to first derive a specification for configuration 
files. We first process a training set of 256 industrial configuration files. This training set of files is
available on-line~\cite{configdataset}. They are mostly correct
but they also may contain some errors.

In order to learn a specification from this large set of configuration
files,
the first step is to 
translate the training set into a more structured typed representation.
We then apply our learning process to learn an abundant set of rules 
specifying various properties that hold on the given training set. 
The learning process is a more expressive form of association rule learning~\cite{agrawal1993mining}, which is used to learn predicate relations between multiple keywords in a configuration file.
